Measuring E-Mail Header Injections on the World Wide Web

### 2016-10-25 Background/history.tex
got it to 9 pages woooooohooooooooo

%TODO Adam: added this para abt E-Mail Header Injection history from CVE
We gathered reported Common Vulnerabilities and Exposures
(CVE)~\cite{cve} to get an idea of the distribution of
reported \ehi over time. We found 28 reports of \ehi, shown in
Table~\ref*{tab:history}. From the table, it can be seen that even though many \ehi vulnerabilities were found in the earlier years (2005-07), there have been several recently discovered \ehi vulnerabilities which suggests that it is still a very real threat and is relevant to modern web security.

>>>>

%TODO Adam: added this para abt E-Mail Header Injection history from CVE
We gathered reported Common Vulnerabilities and Exposures
(CVE)~\cite{cve} to get an idea of the distribution of
reported \ehi over time. We found 28 reports, shown in
Table~\ref*{tab:history}. It can be seen that even though many vulnerabilities were found in the earlier years (2005-07), there have been several recently discovered \ehi vulnerabilities which suggests that it is still a very real and relevant threat to modern web security.

### 2016-10-25 Background/impact.tex
got it to 9 pages woooooohooooooooo

    \noindent\textbf{Denial of Service}
    Denial of service attacks (DoS), can also be caused by exploiting an \ehi vulnerability. The ability to send many \emails by injecting one header field can result in overloading the mail server and cause crashes or instability.

>>>>

    \noindent\textbf{Denial of Service}
    Denial of service attacks (DoS), can also be caused by exploiting an \ehi vulnerability to send excessive \emails resulting in overloading the mail server and cause crashes or instability.

### 2016-10-25 Discussion/limits.tex
got it to 9 pages woooooohooooooooo

		%TODO Adam: added a table here, and explanation about performance tradeoffs with Selenium and bs4.
		A comparison of the running times between the different approaches is shown in Table~\ref{tab:perf}. Because using Selenium results in a slowdown of \slowSelenium, we chose not to do this for performance reasons.

@@

		During the crawl, our system was blacklisted by a few web
        applications (mostly WordPress ones), and Internet Service
        Providers (ISPs). To overcome this, we did two things: (1)
        used an IP range of 60 different IP addresses, and (2) Used a
        blacklist of our own to prevent our Fuzzer from fuzzing web
        application that are known to blacklist automated crawlers.
        However, we could not gather any data about these web
        applications.

@@

        Black-box testing is highly beneficial as explained in Section~\ref{sys:appr}, however it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding as many \texttt{cc} or \texttt{bcc} headers). We must manually notify the developers to get this feedback.

>>>>

		%TODO Adam: added a table here, and explanation about performance tradeoffs with Selenium and bs4.
		A comparison of the running times between the different approaches is shown in Table~\ref{tab:perf}. We chose not to use Selenium as it results in a slowdown of \slowSelenium.

@@

		During the crawl, our system was blacklisted by a few web
        applications (mostly WordPress ones), and Internet Service
        Providers (ISPs). To overcome this, we did two things: (1)
        used an IP range of 60 different IP addresses, and (2) Used a
        blacklist of our own to prevent our Fuzzer from fuzzing
        applications that are known to blacklist automated crawlers.
        This restricted us from gathering data about these
        applications.

@@

        Black-box testing is highly beneficial as explained in Section~\ref{sys:appr}, however it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding many \texttt{cc} or \texttt{bcc} headers). We must manually notify the developers to get this feedback.

### 2016-10-25 Discussion/mitigation.tex
LaTeX tricks to get us down to 9.25
need to cut down 13 lines more woohoo
got it to 9 pages woooooohooooooooo

Using a safe, well tested \email library is the preferred way of
preventing \ehi vulnerabilities (removing the burden of input
sanitization from the developer). A list of known secure libraries for
each language and framework discussed is shown in
Table~\ref{tab:maillib}.
	\begin{table}[tbp]
		\centering
		\scriptsize
		\begin{tabular}{|l|l|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Language}} &
			\multicolumn{1}{c|}{\textbf{Mail Libraries}} \\
			\hline
			PHP & {{PEAR Mail\cite{Hagenbuch2016}, PHPMailer\cite{PHPMailer2016}, Swiftmailer\cite{SwiftMailer2016}}}\\
			\hline
			Python & SMTPLib with email.header.Header\\
			\hline
			Java & Apache Commons E-Mail\cite{ACE2016}\\
			\hline
			Ruby & Ruby Mail \textgreater{}= 2.6\cite{RubyMailGem2016}\\
			\hline
			WordPress & Contact Form 7\cite{CF7}\\
			\hline
		\end{tabular}
		\caption[\titlecap{Mail libraries that prevent e-mail header injection}]{Mail libraries that prevent e-mail header injection.}
		\label{tab:maillib}
	\end{table}

Content management systems such as WordPress and Drupal include
libraries and plugins to prevent \ehi. Thus, websites built with such
CMS' are usually resistant to these attacks. However, it is advised to
use the correct \email plugin, as not all plugins might be secure. An
example of a secure plug-in is included as part of
Table~\ref{tab:maillib}.

If neither of the two options are feasible (website being an in-house
production, or due to lack of support infrastructure), developers can
choose to perform proper input sanitization. Sanitization should be
done keeping in mind RFC5322~\cite{rfc5322}, and care must be taken to
ensure that all edge cases are taken into account.

>>>>

Using a safe, well tested \email library is the preferred way of
preventing \ehi vulnerabilities (removing the burden of input
sanitization from the developer). A list of known secure libraries for
each language and framework discussed is shown in
Table~\ref{tab:maillib}.
	\begin{table}[tbp]
		\centering
		\scriptsize
		\begin{tabular}{|l|l|}
			\hline
			\multicolumn{1}{|c|}{\textbf{Language}} &
			\multicolumn{1}{c|}{\textbf{Mail Libraries}} \\
			\hline
			PHP & {{PEAR Mail\cite{Hagenbuch2016}, PHPMailer\cite{PHPMailer2016}, Swiftmailer\cite{SwiftMailer2016}}}\\
			\hline
			Python & SMTPLib with email.header.Header\\
			\hline
			Java & Apache Commons E-Mail\cite{ACE2016}\\
			\hline
			Ruby & Ruby Mail \textgreater{}= 2.6\cite{RubyMailGem2016}\\
			\hline
			WordPress & Contact Form 7\cite{CF7}\\
			\hline
		\end{tabular}
		\caption[\titlecap{Mail libraries that prevent e-mail header
            injection}]{Mail libraries that prevent e-mail header
          injection.}
        \vspace{-5ex}        
		\label{tab:maillib}
	\end{table}

Content management systems such as WordPress and Drupal include
libraries and plugins to prevent \ehi. Thus, websites built with such
CMS' are usually resistant to these attacks. However, it is advised to
use the correct \email plugin, as not all plugins might be secure. An example of a secure plugin is shown in Table~\ref{tab:maillib}.

If neither of the two options are feasible (in-house
production, or lack of support infrastructure), developers can
choose to perform proper input sanitization. Sanitization should be
done with RFC5322~\cite{rfc5322} in mind to
ensure that all edge cases are covered.

### 2016-10-25 Results/pipeline.tex
got it to 9 pages woooooohooooooooo

\subsection[The Pipeline]{Understanding the Data Pipeline}
%This section serves to represent our pipeline quantitatively and graphically. 
Table~\ref{tab:pipeline} showcases the data gathered by our pipeline, with the differential changes at each stage of the pipeline.

At each stage of the pipeline, the amount of data decreases, for instance, out of the \urls\ URLs we crawled, only \forms\ forms (\formsDelta) were found. Out of these, only \emailforms\ forms (\emailformsDelta) contained e-mail fields.

In our fuzzing attempts, the same behavior is repeated. We fuzzed \fuzzed\ forms with the regular payload, which resulted in a total of \recd\ e-mails (\recdDelta). After analysis of the received e-mails, we further fuzzed \malfuzzed\ forms, which resulted in \success\ e-mails (\successDelta) which contain the vulnerability across \ips IP Addresses corresponding to \domains domains.

%TODO Adam: added the reason for the reduction in the numbers, and accept that we do not have the data to quantify about captcha/csrf
We attribute the difference in the number of forms found to the number of forms fuzzed (a difference of \diffFoundFuzz forms) to the presence of bot-blocking mechanisms on a website (discussed in Section~\ref{limitations}), though we do not know what percentage was caused by the individual bot-blocking mechanisms discussed in Section~\ref{limitations}.

>>>>

\subsection[The Pipeline]{Understanding the Data Pipeline}
%This section serves to represent our pipeline quantitatively and graphically. 
Table~\ref{tab:pipeline} showcases the data gathered by our pipeline, with the differential changes at each stage of the pipeline. At each stage of the pipeline, the amount of data decreases, for instance, out of the \urls\ URLs we crawled, only \forms\ forms (\formsDelta) were found. Out of these, only \emailforms\ forms (\emailformsDelta) contained e-mail fields.

In our fuzzing attempts, the same behavior is observed. We fuzzed \fuzzed\ forms with the regular payload, which resulted in a total of \recd\ e-mails~(\recdDelta). After analysis of the received e-mails, we further fuzzed \malfuzzed\ forms, which resulted in \success\ e-mails (\successDelta) which contain the vulnerability across \ips IP addresses from \domains domains.

We attribute the difference in the number of forms found to the number of forms fuzzed (a difference of \diffFoundFuzz forms) to the presence of bot-blocking mechanisms on a website (discussed in Section~\ref{limitations}), though we do not know what percentage was caused by the individual bot-blocking mechanisms discussed in Section~\ref{limitations}.

### 2016-10-25 System/components.tex
got it to 9 pages woooooohooooooooo

The \Email Field Checker searches for the words \texttt{e-mail},
\texttt{mail} or \texttt{email} within the form, instead of an
explicit HTML5 \email field (e.g.,\ {\lstinline{<input type="email">}}). This is by design, taking into account a common
design pattern used by web developers, where they may have a text
field with an \texttt{id} or \texttt{name} attribute set to
\texttt{email}, instead of an actual \email type attribute, for
purposes of backward compatibility with older browsers. The output of this stage is stored in the database for persistence and acts as the input to the Payload Injection module.

@@

\subsubsection{\Email Form Retriever}
\label{Comp:EMFR}
The \Email Form Retriever is the first stage in the Payload Injection
module. It has the following functions: (1) Retrieve forms and
ensure no duplication occurs before the fuzzing stage, (2) reconstruct
each form's input fields
and values, using the stored form data, and (3) construct the target URL
to create an HTTP request for fuzzing.

>>>>

The \Email Field Checker searches for the words \texttt{e-mail},
\texttt{mail} or \texttt{email} within the form, instead of an
explicit HTML5 \email field (e.g.,\ {\lstinline{<input type="email">}}). This is by design, taking into account a common
design pattern used by web developers, where they may have a text
field with an \texttt{id} or \texttt{name} attribute set to
\texttt{email}, instead of an actual \email type attribute, for
purposes of backward compatibility with older browsers. The output of this stage is stored in the database and acts as the input to the Payload Injection module.

@@

\subsubsection{\Email Form Retriever}
\label{Comp:EMFR}
The \Email Form Retriever is the first stage in the Payload Injection
module. It does the following: (1) Retrieve forms and
remove any duplicates, (2) reconstruct
each form's input fields
and values with the stored form data, and (3) construct the target URL
to create an HTTP request for fuzzing.

### 2016-10-25 introduction.tex
got it to 9 pages woooooohooooooooo

To shed light on this little-studied vulnerability class, we describe
\ehi vulnerabilities and measure \ehi vulnerabilities. To perform this
measurement, we crawled the web, extracted forms with \email fields,
and injected them with different payloads to infer the existence of an
\ehi vulnerability. We then audited received \emails to see if any of
the injected data was present. This allowed us to classify whether a
particular URL was vulnerable to the attack. Our automated system
works in a black-box manner, without looking at the web application's
source code, and only analyzes the payloads of the \emails.

>>>>

To shed light on this little-studied vulnerability class, we describe
\ehi vulnerabilities and measure \ehi vulnerabilities. To perform this
measurement, we crawled the web, extracted forms with \email fields,
and injected them with different payloads to infer the existence of an
\ehi vulnerability. We then audited received \emails to see if any of
the injected data was present. This allowed us to classify whether a
URL was vulnerable to the attack. Our automated system
works in a black-box manner, without looking at the web application's
source code, and only analyzes the payloads in the \emails.

### 2016-10-25 rel_work.tex
got it to 9 pages woooooohooooooooo

In comparison, our work tries to exploit application-level flaws in user input sanitization, which allow us to perform this attack. Our work does not intend to exploit the pipelining mechanism, but to exploit the implementation of the mail function in most popular programming languages, which leaves them with no way to distinguish between user supplied headers and headers that are legitimately added by the application.

@@

Another blog post written by user \lstinline|Voxel@Night|~\cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark. It also showcases the vulnerable code in the plugin that causes the vulnerability. However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage. Neither does it inform the creators of the plugin to fix the discovered vulnerability.
\footnotetext{Note that this plugin is used actively on 300,000 websites (according to~\cite{BestWebSoft2016}), but is yet to be fixed.}
The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}''~\cite{stuttard2011web}. The book, however, does not go into detail on either the attack or the ways to mitigate such an attack. Our work, on the other hand discusses the means to mitigate the attack. We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section~\ref{Comp:Fuzzer}).

To the best of our knowledge, no other research has been conducted to determine the prevalence of this vulnerability across the World Wide Web. We have managed to, on a large scale, crawl and inject web applications with comparatively benign payloads (such as the BCC header) to identify the existence of this vulnerability without causing any ostensible harm to the website. Our injected payloads \emph{do not contain any special characters other than the newline character} and thus cannot cause any unintended consequences. Also, because we are only injecting a payload with the \texttt{bcc} header, the underlying mail servers should not be affected by the additional load. Our work serves to not only prove the existence of the vulnerability on the World Wide Web but to quantify the prevalence.

>>>>

In comparison, our work tries to exploit application-level flaws in user input sanitization, which allow this attack. Our work does not intend to exploit the pipelining mechanism, but to exploit the implementation of the mail function in most popular programming languages, which leaves them with no way to distinguish between user supplied headers and headers that are legitimately added by the application.

@@

Another blog post written by user \lstinline|Voxel@Night|~\cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark. It also showcases the vulnerable code in the plugin that causes the vulnerability. However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage. Neither does it inform the creators of the plugin to fix the discovered vulnerability. Note that this plugin is used actively on 300,000 websites (according to~\cite{BestWebSoft2016}), but is yet to be fixed.
The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook}''~\cite{stuttard2011web}. The book, however, does not go into detail on either the attack or the ways to mitigate such an attack. Our work, on the other hand discusses the means to mitigate the attack. We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section~\ref{Comp:Fuzzer}).

To the best of our knowledge, no other research has been conducted to determine the prevalence of this vulnerability on the World Wide Web. We have managed to, on a large scale, crawl and inject web applications with comparatively benign payloads (the \texttt{bcc} header) to identify the existence of this vulnerability without causing any ostensible harm to the website. Our injected payloads \emph{do not contain any special characters other than the newline character} and thus can't cause any unintended consequences. Also, as we are only injecting the \texttt{bcc} header, the underlying mail servers should not be affected by the additional load. Our work serves to not only prove the existence of the vulnerability on the World Wide Web but to quantify its prevalence.
